MLH1 data report 

### 2017-11-02 rmd_report.rmd
fixed some annoying ordering issues

```{r}
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
kable(AP_strain_table)
```

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci)) + geom_boxplot(data = MLH1_data, aes(fill = factor(strain) ) ) + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "black", "grey", "lightgrey"))
ff <- ff + facet_wrap(~ sex, scales="free")
ff
```

>>>>

```{r}

#set the order of another column, based on another variable (so that when)

MLH1_data <- MLH1_data %>%
  arrange(strain, sex, category, mouse) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match

MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])

# sort your dataframe, by the focal categories
#MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
#kable(AP_strain_table)
```

MLH1_data <- MLH1_data %>%
  arrange(category) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(category),])

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEWES",
                              "WSB", "PWD","MSM","CAST", "HIM", "SPRET"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
ff <- ff   + facet_wrap(~ sex, scales="free")
ff

#
